Comparing MTurk and the US Population's Occupational Diversity

### 2018-11-30 Manuscript.Rmd
Updated code to pull out errors or redundancies.

In 2015, participants’ data were collected from two independently conducted studies (n~1~ = `r nrow(LATech)`; n~2~ = `r nrow(UGA)`). In sample one (n~1~ =`r nrow(LATech)`), occupational data was self-reported by participants who were asked to described their job title. They were then brought to ONET online and asked to retrieve the  six-digit occupational classification code that most closely corresponded to their job title. In the sample two (n~2~ = `r nrow(UGA)`), participants again self-reported their job title. However, the six-digit occupational classification codes were obtained by training research assistants to match the self-reported job titles to those in the ONET database. Using this data, we described the occupational diversity of each sample using relative frequencies of occupational category representation as described by Table 1. Data were again collected in 2017 as part of a separate investigation. In this sample, participants were asked to self-report their occupational data in the manner consistent with sample 1. 
```{r Table 1, results="asis"}
papaja::apa_table(table, 
                  caption = "Proportions of individuals sampled from each intermediate occupational category in 2015.",
                  landscape = TRUE,
                  note = "n = sample; 1 or 2 = sample 1 or 2, accordingly; LL = lower 95% confidence limit; Obs = observed proportion; UL = upper 95% confidence limit.")
```
## Analysis

@@

```{r, echo = FALSE, warning = FALSE, fig.cap = "Comparing the occupational diversity of two MTurk samples with expecations based on the Bureau of Labor Statistics"}
# Bar Plot with error bars
Values <- c(table[1:13,2], table[1:13, 5], table[1:13, 9])
Group <- c("BLS", "BLS", "BLS", "BLS", "BLS", "BLS", "BLS", "BLS", "BLS", "BLS", "BLS", "BLS", "BLS", "Sample 1", "Sample 1", "Sample 1", "Sample 1", "Sample 1", "Sample 1", "Sample 1", "Sample 1", "Sample 1", "Sample 1", "Sample 1", "Sample 1", "Sample 1", "Sample 2", "Sample 2", "Sample 2", "Sample 2", "Sample 2", "Sample 2", "Sample 2", "Sample 2", "Sample 2", "Sample 2", "Sample 2", "Sample 2", "Sample 2")
Occupations <- c(table[1:13, 1])
=======
#Results
  Results shown in our table indicate that MTurk’s occupational frequency distribution does not consistently align with the US economy for both sample 1 ($\chi^2(12) = 368.58, p < .001$) and sample 2 ($\chi^2(12) = 486.07, p < .001$). Examining the 95% confidence intervals across both samples, certain occupations were consistently over- or under-represented. More specifically individuals sampled from MTurk occupied generally more white-collar jobs (e.g., Management, Business, and Financial Occupations; Computer, Engineering, and Science Occupations) and generally fewer blue-collar jobs (e.g., Construction and Extraction Occupations;  Installation, Maintenance, and Repair Occupations; Production Occupations) than what would be expected based on BLS data. For instance, 10.13% of workers in the US economy in 2015 worked in “Management, Business, and Financial Occupations.” By contrast, approximately 17% and 23% of workers from the MTurk samples fell under this classification. These trends were generally consistent across both study 1 and 2.

#- - - - - - - - - - - - - 
#insert table 2 about here
#- - - - - - - - - - - - - 
##Barplot 1
```{r}
#Bar Plot with error bars
require(ggplot2)
Values <- c(Table2[1:13, 5], Table2[1:13, 2])
Group <- c("MTurk", "MTurk", "MTurk", "MTurk", "MTurk", "MTurk", "MTurk", "MTurk", "MTurk", "MTurk", "MTurk", "MTurk", "MTurk", "BLS", "BLS", "BLS", "BLS", "BLS", "BLS", "BLS", "BLS", "BLS", "BLS", "BLS", "BLS", "BLS")
Occupations <- c(Table2[1:13, 1], Table2[1:13, 1])
Occ_Nums <- sapply(strsplit(Occupations, " "), "[[", 1)
barplot_data <- data.frame(as.character(Values), as.character(Occupations),as.character(Group))
names(barplot_data) <- c("Frequency", "Occupations","Group")
dodge <- position_dodge(width = .9)

@@

# Plot data
ggplot(barplot_data, aes(Occupations, Values, fill = Group, ymax = upper, ymin = lower)) + 
  geom_bar(stat="identity", position = "dodge", width = 0.7) +
  geom_bar(stat="identity", position = "dodge", 
                colour = "black", width = 0.7, 
                show.legend = TRUE) +
  scale_y_continuous(breaks = seq(0, 0.30, 0.1), 
                limits = c(0, 0.30), 
                expand = c(0, 0)) +
  scale_fill_manual(name = "Groups" , 
                 values = c('grey30', 'grey60', 'grey 80'), 
                 labels = c("BLS 2015", "Sample 1", "Sample 2")) +
  geom_errorbar(position=position_dodge(width=0.7), 
                     width=0.0, size=0.5, color="black") +
  #ggtitle("Occupational Diversity of MTurk") +
  labs(x = element_blank(), y = "Proportions") +
  theme(legend.position = c(.8,.8), 
        #plot.title = element_text(hjust = 0), 
        text=element_text(family="serif")) +
  coord_flip()
```
## 2015 Demographic Analysis 
## Study 1 Age
```{r}
#Chris's 2015 age analysis 
require(dplyr)

#Load BLS Data
BLS_age_15 <- read_excel("BLS.Age.2015.xlsx")

@@

@@

# Get BLS ethnicity data
=======
##2017 Ethnicity Analysis
```{r}
#Ethnicity Analysis 
#Define obs_eth
BLS_cauc <- as.numeric(BLS_data[7, 4])/100
BLS_AfAm <- as.numeric(BLS_data[7,5])/100
BLS_Asn <- as.numeric(BLS_data[7,6])/100
BLS_Hisp <- as.numeric(BLS_data[7,7])/100
BLS_eth <- c(BLS_AfAm, BLS_Asn, BLS_cauc, BLS_Hisp)

@@

# Ethnicity chi squared test
x4 <- chisq.test(ethnicity_table$n, p = round(ethnicity_table$e,3))
# Result is significant. MTurk is under-represented by African Americans, Asians, and other ethnicities. However, it does appear to be slightly over-represented by Caucasians.

@@

\newpage

# References

```{r Citations, warning = FALSE, echo = FALSE}
r_refs(file = "r-references.bib")
```

\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

>>>>

In 2015, participants’ data were collected from two independently conducted studies (n~1~ = `r nrow(LATech)`; n~2~ = `r nrow(UGA)`). In sample one (n~1~ =`r nrow(LATech)`), occupational data was self-reported by participants who were asked to described their job title. They were then brought to ONET online and asked to retrieve the  six-digit occupational classification code that most closely corresponded to their job title. In the sample two (n~2~ = `r nrow(UGA)`), participants again self-reported their job title. However, the six-digit occupational classification codes were obtained by training research assistants to match the self-reported job titles to those in the ONET database. Using this data, we described the occupational diversity of each sample using relative frequencies of occupational category representation as described by Table 1. Data were again collected in 2017 as part of a separate investigation. In this sample, participants were asked to self-report their occupational data in the manner consistent with sample 1. 
```{r Table 1, results="asis"}
papaja::apa_table(table, 
                  caption = "Proportions of individuals sampled from each intermediate occupational category in 2015.",
                  landscape = TRUE,
                  note = "n = sample; 1 or 2 = sample 1 or 2, accordingly; LL = lower 95% confidence limit; Obs = observed proportion; UL = upper 95% confidence limit.")
```

## Analysis

@@

# Results
  Results shown in our table indicate that MTurk’s occupational frequency distribution does not consistently align with the US economy for both sample 1 ($\chi^2(12) = 368.58, p < .001$) and sample 2 ($\chi^2(12) = 486.07, p < .001$). Examining the 95% confidence intervals across both samples, certain occupations were consistently over- or under-represented. More specifically individuals sampled from MTurk occupied generally more white-collar jobs (e.g., Management, Business, and Financial Occupations; Computer, Engineering, and Science Occupations) and generally fewer blue-collar jobs (e.g., Construction and Extraction Occupations;  Installation, Maintenance, and Repair Occupations; Production Occupations) than what would be expected based on BLS data. For instance, 10.13% of workers in the US economy in 2015 worked in “Management, Business, and Financial Occupations.” By contrast, approximately 17% and 23% of workers from the MTurk samples fell under this classification. These trends were generally consistent across both study 1 and 2.

```{r Barplot, echo = FALSE, warning = FALSE, fig.cap = "Comparing the occupational diversity of two MTurk samples with expecations based on the Bureau of Labor Statistics"}
#Bar Plot with error bars
require(ggplot2)
Values <- c(table[1:13,2], table[1:13, 5], table[1:13, 9])
Group <- c("BLS", "BLS", "BLS", "BLS", "BLS", "BLS", "BLS", "BLS", "BLS", "BLS", "BLS", "BLS", "BLS", "Sample 1", "Sample 1", "Sample 1", "Sample 1", "Sample 1", "Sample 1", "Sample 1", "Sample 1", "Sample 1", "Sample 1", "Sample 1", "Sample 1", "Sample 1", "Sample 2", "Sample 2", "Sample 2", "Sample 2", "Sample 2", "Sample 2", "Sample 2", "Sample 2", "Sample 2", "Sample 2", "Sample 2", "Sample 2", "Sample 2")
Occupations <- c(table[1:13, 1])
Occ_Nums <- sapply(strsplit(Occupations, " "), "[[", 1)
barplot_data <- data.frame(as.character(Values), as.character(Occupations),as.character(Group))
names(barplot_data) <- c("Frequency", "Occupations","Group")
dodge <- position_dodge(width = .9)

@@

# Plot data
ggplot(barplot_data, aes(Occupations, Values, fill = Group, ymax = upper, ymin = lower)) + 
  geom_bar(stat="identity", position = "dodge", width = 0.7) +
  geom_bar(stat="identity", position = "dodge", 
                colour = "black", width = 0.7, 
                show.legend = TRUE) +
  scale_y_continuous(breaks = seq(0, 0.30, 0.1), 
                limits = c(0, 0.30), 
                expand = c(0, 0)) +
  scale_fill_manual(name = "Groups" , 
                 values = c('grey30', 'grey60', 'grey 80'), 
                 labels = c("BLS 2015", "Sample 1", "Sample 2")) +
  geom_errorbar(position=position_dodge(width=0.7), 
                     width=0.0, size=0.5, color="black") +
  #ggtitle("Occupational Diversity of MTurk") +
  labs(x = element_blank(), y = "Proportions") +
  theme(legend.position = c(.8,.8), 
        #plot.title = element_text(hjust = 0), 
        text=element_text(family="serif")) +
  coord_flip()
```
## 2015 Demographic Analysis 
## Study 1 Age
```{r}
#Load BLS Data
BLS_age_15 <- read_excel("BLS.Age.2015.xlsx")

@@

# Get dems
MTurk15 <- read_csv("Demographics.csv")

@@

# Get BLS ethnicity data
```

##2017 Ethnicity Analysis
```{r}
#Ethnicity Analysis 
#Define obs_eth
BLS_cauc <- as.numeric(BLS_data[7, 4])/100
BLS_AfAm <- as.numeric(BLS_data[7,5])/100
BLS_Asn <- as.numeric(BLS_data[7,6])/100
BLS_Hisp <- as.numeric(BLS_data[7,7])/100
BLS_eth <- c(BLS_AfAm, BLS_Asn, BLS_cauc, BLS_Hisp)

@@

# Ethnicity chi squared test
x4 <- chisq.test(ethnicity_table$n, p = round(ethnicity_table$e,3))
# Result is significant. MTurk is under-represented by African Americans, Asians, and other ethnicities. However, it does appear to be slightly over-represented by Caucasians.
```

@@

\newpage
# References
```{r Citations, warning = FALSE, echo = FALSE}
r_refs(file = "r-references.bib")
```
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}
